Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Revise beginning of monte carlo section
This commit makes some minor changes to smooth out the beginning of the
Monte Carlo section.

This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in CCT. The bootstrap CIs obtained compare favorably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter length of the intervals in the specifications implemented.

We adopt the same three data generating processes (DGP) used by CCT to make it easy to compare our results. Also, these DGPs are widely used in the RD literature to evaluate the performance of inference procedures and provide a good testing ground for bias correction due to their exacerbated curvature.

For all Monte Carlo experiments, the pseudo data are generated as 500 i.i.d. draws from:
\begin{align*}
& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
\end{align*}
Regarding the functional form for $\mu(x)$ in each DGP, the first one is based on a fifth order polynomial fitted on the data observed by \cite{lee2008rand} when estimating the incumbency advantage in electoral races to the U.S. House of Representatives. Hence, $\mu_{1}(x)$ is given by,
\begin{align*}
\mu_{1}(x) & = 
\begin{cases}
0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
\end{cases}
\end{align*}

The functional form for $\mu_{2}(x)$, in the second DGP follows the data observed by \cite{ludwig2007}, which we examine in more detail on Section \ref{application}, and follows
\begin{align*}
\mu_{2}(x) & = 
\begin{cases}
3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
\end{cases}
\end{align*}

Finally, the third DGP used in the simulations is given by a modified version of  \cite{lee2008rand} designed to exhibit more curvature and, hence, be more sensitive to the choice of bandwidth in terms of bias. This functional form is the same as used in CCT and serves as an useful example of the effectiveness of the bias correction procedures implemented.
\begin{align*}
\mu_{3}(x) & =
\begin{cases}
0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
\end{cases}
\end{align*}

For each DGP, we used four methods to obtain point estimate and confidence intervals.\footnote{Note that the true value of $\tau$ is $0.04$ for DGPs 1 and 3 and $-3.45$ for DGP 2} For each method, a total 1500 replications were performed. The first two methods follow CCT analytical bias-correction procedure with triangular ($CCT_{tri}$) and uniform ($CCT_{uni}$) kernel, respectively. The third and fourth methods follow the bootstrap procedure proposed in Section \ref{boot} with uniform kernel with ($bootstrap_{uni}$) and without ($bootstrap_{uni}^{naive}$) bias-correction, respectively.

>>>>

This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to the ones obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained compare favorably to the analytical
alternative, with coverage slightly closer to nominal coverage and shorter
length of the intervals in the specifications implemented.

The Monte Calro experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} CCT, which we adopt here to make our simulation results directly
comparable with theirs and more comparable with the rest of the literature. We
will use the same three functional forms for $\mu_j$ as CCT as well.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- candidates who received the largest
vote share in the previous election are the incumbants, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

\nocite{ludwig2007}%
The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
program. Funding eligability is determined at the county level using the
county's historical poverty rate, with a sharp threshold that determines the
provision of services. We use the fifth order polynomial estimated on Ludwig and
Miller's dataset as the conditional expectation for the second DGP:
\begin{equation*}
  \mu_{2}(x) =
  \begin{cases}
    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
    & \textif\ x < 0, \\
    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
    & \otherwise
  \end{cases}
\end{equation*}
and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.

Finally, for the third DGP, we use CCT's modification of $\mu_1$, given by
\begin{equation*}
  \mu_{3}(x) =
  \begin{cases}
    0.48 + 1.27x + 3.59 x^{2} + 14.147 x^3 + 23.694 x^4 + 10.995 x^5
    & \textif\ x < 0 \\
    0.52 + 0.84x - 0.30 x^{2} + 2.397 x^3 - 0.901 x^4 + 3.56 x^5
    & \otherwise
\end{cases}
\end{equation*}
and the population ATE is again $0.04$. CCT introduce this DGP because it has
high curvature and local linear models are likely to exhibit high bias, making
it a natural test case for both their analytical corrections and our bootstrap.

For each DGP, we used four methods to obtain point estimate and confidence intervals. For each method, a total 1500 replications were performed. The first two methods follow CCT analytical bias-correction procedure with triangular ($CCT_{tri}$) and uniform ($CCT_{uni}$) kernel, respectively. The third and fourth methods follow the bootstrap procedure proposed in Section \ref{boot} with uniform kernel with ($bootstrap_{uni}$) and without ($bootstrap_{uni}^{naive}$) bias-correction, respectively.
